Simulations of Ballot Polling Risk-Limiting Audits

### 2023-02-07 providence/ForArchive/sections/appendix.tex

\textbf{Lemma 1.}
For any risk-limit $\alpha \in (0, 1)$, for any margin
and for any round schedule $[n_1, \ldots, n_j]$, 
the \Providence RLA is more efficient than EoR \BRAVO.

>>>>

\textbf{Lemma \ref{lem:efficiency}.}
For any risk-limit $\alpha \in (0, 1)$, for any margin
and for any round schedule $[n_1, \ldots, n_j]$, 
the \Providence RLA is more efficient than EoR \BRAVO.
